%++++++++++++++++++++++++++++++++++++++++
% Don't modify this section unless you know what you're doing!
\documentclass[letterpaper,12pt]{article}
\usepackage{natbib}
\bibliographystyle{apalike}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage{float} % from Jason: better figure control
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
%\usepackage{cite} % takes care of citations
\usepackage{subcaption} % from Jason: subfigures
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}

%++++++++++++++++++++++++++++++++++++++++

\def \N {\mathbb{N}}

\begin{document}

\section{Introduction}
\begin{enumerate}
    \item GCE models
    \begin{enumerate}
        \item Basic ingredients:(SFR, inflow/outflow, yield, SN rate, etc)
        \item Types of GCE models: One-zone: OMEGA; Chemodynamcal models
    \end{enumerate}

    Simple GCE model is enough. Stellar yields make the main differences. (Côté et al. (2017))
    
    \item Evolution of massive stars
        \begin{enumerate}
            \item Different burning phase
            \item supernovae
        \end{enumerate}

    Supernovae is the main production site of Si-29 and Si-30.
    
    \item Presolar Grains
        \begin{enumerate}
            \item Origins of presolar grains: SiC, graphite
            \item types of SiC grains
            \item Silicon isotopic ratio in M grains
            \begin{enumerate}
                \item Enrichment in secondary isotopes and the distribution: heterogeneous GCE 
                \item Slope
            \end{enumerate}
        \end{enumerate}

    C grains from supernovae. M grains contains GCE signature. 

    \item Related works
    \begin{enumerate}
        \item Timmes \& Clayton (1996)
        \item Hoppe et. al. (2009)
    \end{enumerate}
    Changing the nuclear reaction rate might solve the slope problem.
\end{enumerate}

\section{Method}

\begin{enumerate}
    \item Silicon production regions and reactions in supernovae: NUGRID models w/ different 
    \item Nucleosynthesis simulation: ppn
    \item Yield Integration 
    \item GCE simulation: OMEGA+
    \item Monte Carlos setup
\end{enumerate}

\section{Result}
\begin{enumerate}
    \item Trajectory results: compared with C grains 
    \item Integrated yields 
    \item MC result, comparison with M grains
\end{enumerate}

\section{Conclusion}
\end{document}